\myTitle

### 2024-01-11 tex/body-text-of-paper.tex
Rough draft of SNPtype conversion and mapping to genome (stuck at end of microhaplotype discovery section for now).

A number of SNP markers from earlier discovery efforts \citep{clemento2011discovery} had already 
been validated as useful for GSI
and PBT in California \citep{clemento2014evaluation}. These markers were originally assayed
using TaqMan (Life Technologies Corp., Carlsbad, CA) probes or SNPtype assays (CITE).
In order to type these markers using amplicon sequencing, we added Illumina sequencing
primers following the protocol in \citep{campbell2015genotyping}.

@@

>>>>

A number of SNP markers from earlier discovery efforts \citep{clemento2011discovery} had already 
been validated as useful for GSI
and PBT in California \citep{clemento2014evaluation}. These markers were originally assayed
using TaqMan (Life Technologies Corp., Carlsbad, CA) probes or SNPtype assays (CITE).
In order to type these markers using amplicon sequencing, we followed the methods in
\citet{campbell2015genotyping} and added the Illumina small RNA sequencing primer and 
read 2 sequencing primer to the SNPtype Specific Target Amplification Primer and Locus 
Specific Primers respectively.  We then dropped any loci that produced genotypes that were 
frequently inconsistent with genotypes produced with the SNPtype assays and any loci that 
did not amplify well or took over PCRs when run with the other loci in the panel.  We then 
used Freebayes \citep{garrison2012haplotype} to identify non mulltinucleotide or complex variants
in addition the the SNPs targeted by the original TaqMan assays.

@@

After we designed these loci, we compiled the reference sequences for these and the
other loci and mapped them to the Chinook v1.0 genome assembly \citep{christensen2018chinook}
with both the Burrows-Wheeler Aligner (CITE) and the BLAST-like Alignment tool \citep{kent2002blat}.
Genome locations found with both aligners were assumed to be the most likely locations
of these target amplicons in the genome.
